Parameter estimation in biochemical models

### 2017-12-05 Paper_v7.tex
adding last figures

\subsection*{Additional file S6-(Comparison of DOPS to ESS)}
\begin{figure}
\includegraphics[width=1.00\textwidth]{./rachelfigs/fig_s5-crop} %fix me
  \caption{Mean convergence curves for DOPS and ESS for (a) CHO model  (b) coagulation with $\mathcal{T}$ = 25 trials per method.}%
    \label{fig-compare-DOPS-ESS}%
\end{figure}

>>>>

\subsection*{Additional file S6-(Comparison of DOPS to ESS)}
\begin{figure}
\includegraphics[width=1.00\textwidth]{./rachelfigs/fig_s5-crop}
  \caption{Mean convergence curves for DOPS and ESS for (a) CHO model  (b) coagulation with $\mathcal{T}$ = 25 trials per method.}%
    \label{fig-compare-DOPS-ESS}%
\end{figure}

\subsection*{Additional file S7-(Dispersion Curves)}
\begin{figure}
\includegraphics[width=1.00\textwidth]{./rachelfigs/dispersion_curves-crop}
    \caption{Dispersion curves for DOPS on (a) CHO model (b) coagulation with $\mathcal{T}$ = 25 trials per problem .}%
    \label{fig-DOPS-Dispersion-Curves}%
\end{figure}

\subsection*{Additional file S8-(Comparison of functional values)}
\begin{figure}
\includegraphics[width=1.00\textwidth]{./rachelfigs/compare_functional_vals-crop}
    \caption{Variability  analysis in best objective value for $\mathcal{T}$ = 25 trials. (a) Ackley  300 dimensional (b) Rastrigin 300 dimensional (c) CHO model (d) coagulation. }%
    \label{fig-DOPS-Variability}%
\end{figure}
